Process-based phenotypes: an application to the ontology of cell physiology

### 2011-11-28 paper/drinking.tex

\begin{table*}
  \centering
  \begin{tabular}{l|l|l|l}
    & Increased cytoplasmic flow rate & Normal cytoplasmic flow rate & Decreased
    cytoplasmic flow rate \\
    \hline
    Increased frequency &increased total flow rate &increased total
    flow rate &?\\
    Normal frequency &increased total flow rate &normal total flow
    rate &decreased total flow rate\\
    Decreased frequency &?&decreased total flow rate &decreased total
    flow rate\\
    \hline
  \end{tabular}
  \caption{\label{tbl:flow}Total cytoplasmic flow rate...}
\end{table*}

>>>>

\begin{table*}
  \centering
  \begin{tabular}{l|l|l|l}
    & Increased cytoplasmic flow rate & Normal cytoplasmic flow rate & Decreased
    cytoplasmic flow rate \\
    \hline
    Increased frequency &increased total flow rate &increased total
    flow rate &?\\
    Normal frequency &increased total flow rate &normal total flow
    rate &decreased total flow rate\\
    Decreased frequency &?&decreased total flow rate &decreased total
    flow rate\\
    \hline
  \end{tabular}
  \caption{\label{tbl:flow}Interdependency for the attribute {\em
      Total cytoplasmic flow rate}. Depending both on whether the
    cytoplasmic flow rate in individual {\em cytoplasmic streaming}
    processes is increased or decreased and whether the frequency of
    occurrence of {\em cytoplasmic streaming} is increased or
    decreased, the total cytoplasmic flow rate can be increased or
    decreased.}
\end{table*}
